AHABus \& FCORE: A Modular Bus System for High-Altitude Balloon Missions

### 2017-04-25 chapters/01-introduction.tex
Proof read introduction

For applications that require low atmospheric density or medium altitudes, but do not depend on the payload being in a \acrfull{leo}, \acrfull{hab} present an affordable alternative. Such balloons, inflated with low-density gases (usually helium or hydrogen), can reach the stratosphere (altitudes of 30 to 45km). The payload is encased in a thermally insulated container attached under the balloon itself. Depending on the mission, balloons either float at a constant altitude and drift for long durations or climb to the target altitude, then burst under the pressure of the expanding gas. Once the balloon is destroyed, the payload is brought back to the ground under a parachute.

The main component of the payload is the \acrfull{obc}, which controls the different instruments through the different phases of flight (ascent, observation, free-fall and parachute descent). Because high-altitude winds can reach speeds upwards of 150km/h and carry the payload over long distances, most balloons carry a \acrfull{gnss} receiver that the OBC can use to keep track of the balloon's position and altitude. To avoid loosing flight data if the payload is lost or lands in an unaccessible area, the OBC also controls a radio transmission system used to forward payload data and metadata (\acrshort{gnss} coordinates, altitude, systems health) to a ground station as it is acquired.

@@

The satellite industry solves this problem by making use of buses for most missions. Instead of designing a custom, monolithic platform for each new satellite, manufacturers sell buses that provide utility (power, data bus, attitude control and space-to-ground communications) to which the customer or science team connect mission-specific payloads.

@@

In the following chapters, the current state of \acrlong{hab} and nano-satellite mission architectures is discussed. The proposed platform is then presented, followed by the results of the evaluation, and finally a critical discussion of those results and the overall performance of the platform.

>>>>

For applications that require low atmospheric density or medium altitudes, but do not depend on the payload being in a \acrfull{leo}, High-Altitude Balloons (\acrshort{hab}) present an affordable alternative. Such balloons, inflated with low-density gases (usually helium or hydrogen), can reach the stratosphere (altitudes of \SI{30}{\kilo\metre} to \SI{45}{\kilo\metre}). The payload is encased in a thermally insulated container attached under the balloon itself. Depending on the mission, balloons either float at a constant altitude and drift for long durations or climb to the target altitude, then burst under the pressure of the expanding gas. Once the balloon is destroyed, the payload is brought back to the ground under a parachute.

The main component of the payload is the \acrfull{obc}, which controls the different instruments through the different phases of flight (ascent, observation, free-fall and parachute descent). Because high-altitude winds can reach speeds upwards of \SI{150}{\kilo\metre\per\hour} and carry the payload over long distances, most balloons carry a \acrfull{gnss} receiver that the OBC can use to keep track of the balloon's position and altitude. To avoid loosing flight data if the payload is lost or lands in an unaccessible area, the OBC also controls a radio transmission system used to forward payload and ancillary data (\acrshort{gnss} co-ordinates, altitude, systems health) to a ground station as it is acquired.

@@

The satellite industry solves this problem by making use of buses for most missions. Instead of designing a custom, monolithic platform for each new satellite, manufacturers sell buses that provide common utilities (power, data bus, attitude control and platform-to-ground communications) to which the customer or science team connect mission-specific payloads.

@@

The current state of \acrlong{hab} and nano-satellite mission architectures is first discussed in chapter \ref{ch:literature-review}. The proposed platform, \acrshort{ahabus}, and the development process that led to its design are then presented in chapter \ref{ch:methodology}. Finally, chapters \ref{ch:results} and \ref{ch:discussion} present the results of the prototype's testing and show that the project was overall successful, even though more testing will be required to qualify the \acrshort{ahabus} platform for flight.
